---
title: COVID-19 situations of Japan
author: Jinhao Luo
date: "`r Sys.Date()`"
slug: etc5523-blog-1
categories: []
tags: []
subtitle: Exploring the situation of COVID-19 in Japan
summary: This post will explore the situation of COVID-19 in Japan
authors: []
lastmod: "`r Sys.time()`"
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
bibliography: references.bib
biblio-style: apa
output: 
  bookdown::html_document2:
    citation_package: biblatex
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, cache=FALSE, message=FALSE, warning=FALSE)

library(tidyverse)
library(kableExtra)
library(tibble)
library(lubridate)
library(widgetframe)
library(DT)
library(htmltools)
```

```{r data}
# install.package("devtools")
# devtools::install_github("RamiKrispin/coronavirus")

library(coronavirus)
data("coronavirus")
# update_dataset() 
# You can use this function to update the coronavirus package, but this post will use the version 0.3.0.9000 of package to write the data story.
```




# Introduction

@iwasaki2020does indicates that although Japan has a dense and aging population, it still reported low cases of COVID-19 infection in the first few months of the COVID-19 outbreak, compared with other countries. However, according to the latest [COVID-19 report](https://www.mhlw.go.jp/content/10900000/000666371.pdf) from the Ministry of Health, Labour and Welfare of Japan, Japan has experienced the second outbreak of COVID-19 from July 2020 (@Japan). And it is more serious than the first one. Therefore, this post will focus on the COVID-19 cases of Japan. 

# Data description

For exploring the COVID-19 situations of Japan, the post has used the COVID-19 data from the package called **coronavirus**. This package is from the Github repository owned by Rami Krispin, which could find all information related to this package from  [Github](https://github.com/RamiKrispin/coronavirus). By glimpsing this data, there are 175055 observations and 7 variables. Based on the help page of the coronavirus package, @coronavirus indicate the variables are in the following table \@ref(tab:variable-table):

```{r variable-table}
tribble(~Variable, ~Class, ~Description,
        "date", "Date", "The format of date is YYYY-MM-DD",
        "province", "character", "Name of province or state, if provided",
        "country", "character", "Name of country or region",
        "lat", "numeric", "Latitude of center of geographic region",
        "long", "numeric", "Longitude of center of geographic region",
        "type", "character", "Type of cases (confirmed, death, recovered)",
        "cases", "integer", "Number of cases on given date") %>% 
  kable(caption = "Description of variables in coronavirus data") %>% 
  kable_styling(bootstrap_options = c("hover", "striped", "condensed"), position = "center")
```

Because this post will focus on the cases of Japan, the **filter** function will be used to filter the data which makes the data only include Japan's cases. Besides, because the types of COVID-19 cases are all contained in the same column, the function call **pivot_wider** will be applied to change the position of type as a variable rather than value.

# Data story

```{css style-table, echo = FALSE}

.table.table-striped.table-hover, .table thead th {
  font-size: 5px;
}

```

```{r summary-table}
# filter the Japan's cases and change the format of table
covid_19_japan <- coronavirus %>%
  filter(country == "Japan") %>% 
  select(-province, -lat, -long) %>%
  pivot_wider(names_from = "type", values_from = "cases") %>%
# Extract the year and month in order to calculate the cases base on month.
  mutate(year = year(date), month = month(date)) %>% 
  group_by(year,month) %>%
# Calculate the cases of each month
  summarise(confirmed = sum(confirmed),
            death = sum(death),
            recovered = sum(recovered)) %>%
# calculate the cumulative number of cases.
  ungroup() %>% 
  mutate(total_confirmed = cumsum(confirmed),
         total_death = cumsum(death),
         total_recovered = cumsum(recovered)) %>%
# Rename the variables' name to make better understanding
  rename(`monthly confirmed` = "confirmed",
         `monthly death` = "death",
         `monthly recovered` = "recovered",
         `cumulative confirmed` = "total_confirmed",
         `cumulative death` = "total_death",
         `cumulative recovered` = "total_recovered") 

covid_19_japan_table <- covid_19_japan %>% 
  kable(caption = "Summary table of COVID-19 cases in Japan") %>% 
  kable_styling(bootstrap_options = c("striped", "hover"), 
                full_width = FALSE, 
                font_size = 16, 
                latex_options = "scale_down") %>% 
  column_spec(6:8, bold = T)


covid_19_japan_table
```


In order to explore the COVID-19 situations of Japan and identify the second outbreak situation, a summary table has been generated to support the following explanation. Table \@ref(tab:summary-table) indicates the monthly cases and cumulative cases of Japan from the first patient have been confirmed to the end of August 2020. Based on table \@ref(tab:summary-table), there were little cases in the first three month in Japan, which were only 2255 total cases and just account for `r round((covid_19_japan[3,]["cumulative confirmed"]/covid_19_japan[8,]["cumulative confirmed"])*100,2)`% of the total confirmed cases. The first outbreak happened in April of 2020, which reported 12029 cases increased in this month, and the total cases have jumped to 14284 cases. The confirmed cases of April have increased `r round(((covid_19_japan[4,]["monthly confirmed"]-covid_19_japan[3,]["cumulative confirmed"])/covid_19_japan[3,]["cumulative confirmed"])*100, 2)`% compared with the first three month total confirmed cases. Fortunately, the monthly confirmed cases of May and June all gradually decreased, and the total confirmed cases have slowly increased. However, May has reported the highest mortality among the eight months. There were 417 death cases in May, and it even three cases higher than that of the first outbreak, which was 414 cases. The reason might because the outbreak in April resulted in high confirmed cases so that led to the highest mortality in May. But, fortunately, the monthly recovered cases in May was 11882, and the cumulative recovered cases have reached to 14342, which accounted for `r round((covid_19_japan[5,]["cumulative recovered"]/covid_19_japan[5,]["cumulative confirmed"])*100, 2)`% of the cumulative confirmed cases. And the recovery rate of June has reached to `r round((covid_19_japan[6,]["cumulative recovered"]/covid_19_japan[6,]["cumulative confirmed"])*100, 2)`%. 
 
However, because of the gradual return to works or the consciousness of defenses for COVID-19 of people may already be worn down. Japan also experienced the same second COVID-19 outbreak like other countries. The monthly confirmed cases of July have recorded at 17619, which increased `r round(((covid_19_japan[7,]["monthly confirmed"]-covid_19_japan[6,]["monthly confirmed"])/covid_19_japan[6,]["monthly confirmed"])*100, 2)`% over June. Furthermore, August has recorded the highest monthly confirmed cases within eight months, which were 32162 cases. Such high monthly cases have contributed to the dramatic increase in cumulative confirmed cases of August which were 68396. And the monthly confirmed rate of August has accounted for almost a half among the total cases in eight months, which was `r round((covid_19_japan[8,]["monthly confirmed"]/covid_19_japan[8,]["cumulative confirmed"])*100, 2)`%. Fortunately, there were only 36 death cases and 290 death cases in July and August, respectively. In addition, the recovered cases in July and August were also high, which were 8316 and 31564 cases, respectively. Finally, there are `r round((covid_19_japan[8,]["cumulative recovered"]/covid_19_japan[8,]["cumulative confirmed"])*100, 2)`% of patients have reported as recovery at the end of August. That should be good news for Japan. 

# Interactive table 

For helping the readers to better realise the COVID-19 situation of Japan. An interactive table has been created for the readers to explore the data of COVID-19 in Japan. Please refer to the following Figure \@ref(fig:DT-table).


```{r DT-table, fig.cap="The interactive table of COVID-19 situations in Japan", out.width='100%'}
interactive_table <- coronavirus %>% 
  filter(country == "Japan") %>%
  select(-province, -lat, -long) %>%
  pivot_wider(names_from = "type", values_from = "cases") %>%
  mutate(total_confirmed = cumsum(confirmed),
         total_death = cumsum(death),
         total_recovered = cumsum(recovered)) %>%
  rename(`daily confirmed` = "confirmed",
         `daily death` = "death",
         `daily recovered` = "recovered",
         `cumulative confirmed` = "total_confirmed",
         `cumulative death` = "total_death",
         `cumulative recovered` = "total_recovered") 

frameWidget(datatable(interactive_table, 
                      class = "display",
                      extensions = "FixedColumns",
                      caption = tags$caption(style = "caption-side: bottom; text-align: center;",
                                             "Daily COVID-19 cases of Japan (interactive table)"),
                      width = "100%",
                      height = 600,
                      filter = 'top', 
                      options = list(pageLength = 5, 
                                     autoWidth = TRUE,
                                     scrollX = TRUE)))

```

# Conclusion

Many countries have experienced the second COVID-19 outbreak nowadays, as well as Japan. Everyone still needs to keep their consciousness of defense this pandemic. Furthermore, hoping the novel coronavirus vaccine will come out as soon as possible, as well as there is no increasing trend of confirmed cases in Japan.

# Acknowledgement

For the reproducibility of this post, You can find the relevant information of **coronavirus** package in this [Github repository](https://github.com/RamiKrispin/coronavirus). In addition, the versions of R and packages which used in this post would be listed in the following. 

The programming language used to write the data story of COVID-19 in Japan is R (4.0.2) [@R]. Following packages has been included in our scripts:


- package coronavirus (0.3.0.9000) [@coronavirus],
- package tidyverse (1.3.0) [@tidyverse],
- package kableExtra (1.1.0) [@kableExtra],
- package tibble (3.0.3) [@tibble],
- package lubridate (1.7.9) [@lubridate],
- package widgetframe (0.3.1) [@widgetframe],
- package DT (0.15) [@DT],
- package htmltools (0.5.0) [@htmltools]

# References