---
title: COVID-19 situations of Japan post 2
author: Jinhao Luo
date: "`r Sys.Date()`"
slug: etc5523-blog-1
categories: []
tags: []
subtitle: Exploring the additional information of COVID-19 in Japan
summary: This post will explore the additional information of COVID-19 in Japan
authors: []
lastmod: "`r Sys.time()`"
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
bibliography: references.bib
biblio-style: apa
output: 
  bookdown::html_document2:
    citation_package: biblatex
---
<style>
body{
text-align: justify
}
h1 {
text-align: left
}
h2{
text-align: left
}
</style>


```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, cache=FALSE, message=FALSE, warning=FALSE)

library(tidyverse)
library(ggplot2)
library(dplyr)
library(plotly)
library(lubridate)
library(DT)
library(widgetframe)
library(htmltools)
```

```{r data}
# install.package("devtools")
#devtools::install_github("RamiKrispin/coronavirus")
# You need to install the coronavirus package first

#library(remotes)
#remotes::install_github("GuangchuangYu/nCov2019", dependencies = TRUE)
# Download the nCov2019 package for analyse the cities of Japan


library(coronavirus)
covid_19 <- refresh_coronavirus_jhu()
# use the refresh_coronavirus_jhu() function to pull the latest data of coronavirus package.

library(nCov2019)
nCov2019_set_country('Japan')
get_data <- load_nCov2019(lang = 'en', source = 'github')
city_Japan <- get_data['province']
```

```{r data-wrangling}
covid_japan <- covid_19 %>% 
  select(-location_type, -location_code,-location_code_type) %>%
  rename("country" = "location",
         "type" = "data_type") %>%
  filter(country == "Japan") %>%
  arrange(date) %>% 
  drop_na() %>% 
  mutate(type = 
           case_when(
             str_detect(type, "cases_new") ~ "confirmed",
             str_detect(type, "deaths_new") ~ "death",
             str_detect(type, "recovered_new") ~ "recovered"))

```

# Introduction

As mention in the [first blog post](https://etc5523-jinhao-blog-post.netlify.app/post/covid_19_japan/etc5523-blog-1/) last two weeks ago, Japan has experienced the second outbreak from July 2020, which would generate some negative influences to the country. But how is the situation of COVID-19 in Japan developing for the past two weeks? Therefore, this post will continue to focus on tracking the cases of COVID-19 in Japan based on the first post. However, the first post only uses the statistical tables to support the analysis, which might not be sufficient and comprehensive. Therefore, this post will create some plots to illustrate the pandemic in Japan to show clearer trends and compare. 

This post will focus on the overall situation of COVID-19 in Japan first, to identify the general trends of total confirmed cases, total recovered cases, as well as the total mortality in order to evaluate the current condition. After that, the post will go further to analysis the pandemic trend of each city in Japan, as well as make the comparison in order to filter out the most serious area in Japan.


# Data stories

## The overall situation of COVID-19 in Japan

Figure \@ref(fig:cumulative-plot) shows the trends of the total confirmed, recovered, and death cases of Japan from the first patient has been confirmed to 16/09/2020. It is clear that the total confirmed cases and recovered cases have a similar trend during the period. While, the trend of total death cases is flat, which should be a fortunate condition in this pandemic. The first outbreak happens on 01/04, which has experienced a significant increase from around 5000 confirmed cases to around 15000 cases in a month. After that, the trend changed to be moderate, which seems likely that the pandemic has been controlled. Many patients have recovered since 01/05. The total recovered cases increased dramatically until 01/06, which has recorded around 15000 persons. 

However, two months later, Japan has experienced the second outbreak of COVID-19. The trend of total confirmed cases has changed and experienced a rapid rise since 01/07. Until 16/09, the total confirmed cases have recorded over 75000 persons. This increase was more significant and longer than the first one. However, it is clear that the total recovered rate also follows a similar trend of the total confirmed cases in the second outbreak, which might indicate that the medical system and therapy of Japan have sufficient abilities to handle COVID-19, and hospitals could help patients to recover as soon as possible.

Furthermore, Japan has recorded low mortality during the pandemic. By comparing with Figure \@ref(fig:daily-plot) which shows the daily cases in Japan, the daily death cases were never over 30 people per day, which could show the world-class of the Japanese medical system. Besides, Figure \@ref(fig:daily-plot) could also help readers easier to evaluate the total confirmed cases and recovery. 11/04 and 30/07 are the two daily confirmed cases peak of two outbreaks, which have recorded 701 and 1762, respectively. Meanwhile, 10/05 was the first peak of daily recovered rate which was 2221 persons, while 15/08 was the second peak which indicated 3941 persons have recovered on that day. Interestingly, 14/08 has recorded a negative daily recovery which was -693. A reason may be the recording mistake required to remove 693 people from the total recovered rate. In addition, since 15/08, the daily recovered cases, in general, higher than the daily confirmed cases, which could indicate the gap between the confirmed cases and recovered cases was reducing, the recovery rate might meet the confirmed rate and the pandemic might disappear.

```{r cumulative-plot,fig.cap="Total confirmed, recovered, and deadth cases of COVID-19 in Japan (22/01/2020-16/09/2020)"}
cumulative_plot <- covid_japan %>% 
  pivot_wider(names_from = "type", values_from = "value") %>%
  mutate(cumulative_confirmed = cumsum(confirmed),
         cumulative_death = cumsum(death),
         cumulative_recovered = cumsum(recovered)) %>% 
  pivot_longer(c("cumulative_confirmed",
                 "cumulative_death",
                 "cumulative_recovered"),
               names_to = "cumulative_type",
               values_to = "cumulative_cases")

cumulative_plot %>%
  ggplot(aes(date, 
             cumulative_cases, 
             colour = cumulative_type)) +
  geom_line() +
  scale_x_date(date_breaks = "1 month", date_labels = "%d/%m") + scale_y_continuous(breaks = c(5000, 10000, 20000, 30000, 40000, 50000, 60000, 70000, 80000)) + 
  xlab("Date (dd/mm)") + 
  ylab("Total cases") + 
  #scale_colour_manual(values = c("black", "green", "blue")) + 
  scale_colour_manual(name = "type",
                      labels = c("confirmed",
                                   "death",
                                   "recovered"),
                      values = c("red", "green", "blue")) +
  theme_bw() + 
  theme(legend.position = "top")
  

```

```{r daily-plot, fig.width = 7.5, fig.cap="Interactive plot of daily confirmed, recovered , and death cases of COVID-19 in Japan (22/01/2020-16/09/2020)"}
daily_plot<- covid_japan %>% 
  ggplot(aes(date, 
             value, 
             shape = type,
             colour = type)) +
  geom_point() + 
  geom_line() +
  scale_x_date(date_breaks = "1 month", date_labels = "%d/%m") +
  theme(legend.position = "bottom") + 
  xlab("Date (dd/mm)") + 
  ylab("cases") +
  theme_bw() + 
  scale_colour_manual(values = c("red", "green", "blue"))


ggplotly(daily_plot) %>% layout(legend = list(orientation = "h"))
```

## COVID-19 situation of cities in Japan

After evaluating the general situation of COVID-19, further analysing would be conducted in this section. Figure \@ref(fig:find-top-six) is an interactive table that shows the latest COVID-19 data (15/09/2020) of each city in Japan. The cities on the first page are the top six cities that have the highest confirmed cases. This section would focus on six cities to analyse the condition of COVID-19.

```{r find-top-six, fig.cap="The latest total cases of confirmed, recovered, and death of each city in Japan (in 15/09/2020)"}
city_cum <- city_Japan %>% 
  filter(time == max(time)) %>% 
  mutate(day = day(time),
         month = month(time),
         `date(dd/mm)` = paste0(day, "/0", month)) %>% 
  rename("confirmed" = "cum_confirm",
         "recovered" = "cum_heal",
         "death" = "cum_dead",
         "city" = "province") %>% 
  dplyr::select(`date(dd/mm)`, city, confirmed, recovered, death) 

frameWidget(datatable(city_cum,
                      extensions = "FixedColumns",
                      caption = tags$caption(style = "caption-side: top; text-align: left;",
                                             "The latest total number of cases of each city in Japan"),
                      filter = 'top', 
                      options = list(pageLength = 6, 
                                     autoWidth = TRUE)))
```

Figure \@ref(fig:top-six-plot) shows the COVID-19 condition of the first six highest confirmed cases of cities in Japan. However, by browsing that plot, and compared with the Figure \@ref(fig:cumulative-plot), we found that the figures of Figure \@ref(fig:top-six-plot) since June might not be credible because the trend of all cases never changed, while the total cases have still experienced an increasing trend in Japan. Therefore, the section would only focus on the first outbreak of COVID-19 in Japan, which was the period from January to May. 

Tokyo has accounted for the highest total confirmed cases among the six cities, which may be the high dimension of the population in Tokyo city. In addition, Osaka is the city with the second-highest total confirmed cases which were almost 2000 persons. While the rest countries have similar total confirmed cases which were around 1000 persons. 

In addition, Osaka, Kanagawa, Hokkaido, Saitama, and Chiba have similar total mortality which was less than 500 persons. Tokyo, however, has the highest mortality because of the highest confirmed cases. Furthermore, Tokyo and Osaka were the two cities with the highest recovery rate which were around 3600 and 1400, respectively. The city of Kanagawa and Saitama has similar recovered cases which were around 1000 persons. While the city of Chiba and Hokkaido have accounted for the least recovery rate which was over 500 persons during the five months. 

```{r top-six-plot, fig.cap="Total confirmed, recovered, and death cases of COVID-19 of the first six highest confirmed cases cities (15/03/2020-13/09/2020)"}
city_Japan %>%
  filter(province %in% c("Tokyo", "Osaka", "Kanagawa", "Hokkaido", "Saitama", "Chiba")) %>%
  rename("total_confirmed" = "cum_confirm",
         "total_recovered" = "cum_heal",
         "total_death" = "cum_dead") %>% 
  pivot_longer(c("total_confirmed", "total_recovered", "total_death"),
               names_to = "type",
               values_to = "cases") %>% 
  ggplot(aes(time, cases, group = province, colour = province)) + 
  geom_line() + 
  facet_grid(type~province) + 
  theme_bw() +
  theme(legend.position = "top") +
  theme(axis.text.x = element_text(angle =90,vjust = 0.5)) + 
  scale_colour_discrete(name = "city") + 
  scale_x_date(date_breaks = "1 month", date_labels = "%m") +
  xlab("Date (month)") 
  
```

```{r eval=FALSE}
t <- city_Japan %>%
  filter(city %in% c("Tokyo", "Osaka", "Kanagawa", "Hpkkaido", "Saitama", "Chiba")) %>% 
  pivot_longer(c("cum_confirm", "cum_dead", "cum_heal"),
               names_to = "type",
               values_to = "cases")
library(scales)
require(scales)
require(ggplot2)
fsl <- facetshade(data = t, 
                  aes(time, cases), f = .~city)

fsl+geom_line(colour = alpha("black", 0,05)) + 
  geom_line(data = t, colour = "red") + 
  facet_wrap(f = ~city) + theme(lengend.position = "none")
```

# Conclusions

In general, Japan has still experienced the increasing trends of confirmed cases. However, the daily recovery rate has overtaken the daily confirmed cases since the middle of August, which might show a piece of positive information because the recovered people were more than the confirmed patients. It might implicate that Japan was experiencing the process of recovery. In addition, Tokyo and Osaka were the most serious cities in the first outbreak of COVID-19. Although the city of Kanagawa, Hokkaido, Saitama, and Chiba also accounted for the first six highest confirmed case, the confirmed, and death cases were low compared with the top two cities.

# Acknowledgement

This post has used two datasets for carrying out the analysis. The first one is from [coronavirus](https://github.com/RamiKrispin/coronavirus) package, which is used for doing the evaluation of the general trend of COVID-19 in Japan. And the second one is from [nCov2019](https://github.com/GuangchuangYu/nCov2019) package, which is used for analysing the COVID-19 condition of cities in Japan. Click the link and you can get more details from the websites.

The programming language used to write the data stories of COVID-19 in Japan is R (4.0.2) [@R]. Following packages has been included in the scripts:

- package tidyverse (1.3.0) [@tidyverse],
- package ggplot2 (3.3.2) [@ggplot2],
- package dplyr (1.0.1) [@dplyr],
- package plotly (4.9.2.1) [@plotly],
- package lubridate (1.7.9) [@lubridate],
- package DT (0.15) [@DT],
- package widgetframe (0.3.1) [@widgetframe],
- package htmltools (0.5.0) [@htmltools],
- package coronavirus (0.3.0) [@coronavirus],
- package nCov2019 (0.3.6) [@nCov2019]

# References